### 2023-03-24 reachable-resilience.tex
Up

The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong upward compatibility (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}). Hence reachable-resilience is decidable for Petri nets and VASS.
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.

@@

Since VASS are WSTS with strong upward compatibility and since there is an algorithm that computes a finite basis of  $\uparrow post^*(S)$, \cite{DBLP:conf/gg/Ozkan22} deduced that bounded reachable-resilience is decidable for VASS, hence reachable-resilience is decidable for VASS. \alain{resilience decidable for LCS ? LCS sont-ils strong (quelle sémantique ?) et $\uparrow post^*(S)$ is computable ?}

>>>>

The characterization is used to show that Petri nets are $\post^*$-effective. It is well-known that Petri nets constitute WSTS with strong upward compatibility (Thm.~6.1 in \cite{DBLP:journals/tcs/FinkelS01}). 
Since VASS are WSTS with strong upward compatibility and since there is an algorithm that computes a finite basis of  $\uparrow \post^*(S)$, \cite{DBLP:conf/gg/Ozkan22} deduced that bounded reachable-resilience is decidable for VASS.
Hence reachable-resilience is decidable for Petri nets and VASS.
However, the hypothesis that $\uparrow \post^*$ is computable cannot be tested in the general WSTS framework.

@@

 \alain{resilience decidable for LCS ? LCS sont-ils strong (quelle sémantique ?) et $\uparrow post^*(S)$ is computable ?}
